\documentclass[letterpaper, 12pt]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{sectsty}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT CONFIGURATION
%----------------------------------------------------------------------------------------

\def\name{Roc Armenter}
\def\footerlink{https://rocarm.github.io/}

% Metadata
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, monetary policy, finance, Machine Learning},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

% Margins
\geometry{
  body={6.0in, 8.5in},
  left=1.25in,
  top=1.0in
}

% Headers
\pagestyle{myheadings}
\markright{\name \hspace*{.25em} (Curriculum Vitae)}
\thispagestyle{empty}

% Section Fonts
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% No indentation
\setlength\parindent{0em}

% Custom lists
\newenvironment{itemize2}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{2em}
  }
}{
  \end{list}
}

%----------------------------------------------------------------------------------------
%	CV CONTENT
%----------------------------------------------------------------------------------------

\begin{document}

% Header
\begin{center}
  \Huge \textbf{\name} \\
  \smallskip
  \large Visiting Scholar, The Wharton School \\
  \large Executive Vice President and Economist, Federal Reserve Bank of Philadelphia
\end{center}

\vspace{0.1in}

\begin{center}
  \begin{tabular}{rl}
    \textbf{Email:} & \href{mailto:roc.armenter@phil.frb.org}{\tt roc.armenter@phil.frb.org} \\
    \textbf{Website:} & \href{https://rocarm.github.io/}{\tt rocarm.github.io} \\
  \end{tabular}
\end{center}

\section*{Education}

\begin{itemize2}
  \item \textbf{Ph.D. in Economics}, Northwestern University, 2004.
  \item \textbf{M.Sc. in Economics}, Universitat Pompeu Fabra, 1999.
  \item \textbf{B.A. in Economics}, Universitat Pompeu Fabra, 1998.
\end{itemize2}

\section*{Research Fields}

\begin{itemize2}
    \item Monetary Policy, Macroeconomics, and Finance.
    \item Artificial Intelligence, Machine Learning, and Applied Category Theory.
\end{itemize2}

\section*{Academic \& Professional Positions}

\begin{itemize2}
\item \textbf{The Wharton School (University of Pennsylvania)}
\begin{itemize2}
  \item Visiting Scholar, Finance Department, 2026--present.
\end{itemize2}

\smallskip

\item \textbf{Federal Reserve Bank of Philadelphia}
\begin{itemize2}
  \item Executive Vice President and Economist, 2022--present.
  \begin{itemize}
    \item Director of Research and Consumer Finance Institute, 2022--2025.
  \end{itemize}
  \item Vice President and Economist, 2014--2022.
  \item Senior Economic Advisor and Economist, 2013--2014.
  \item Economic Advisor and Economist, 2011--2013.
  \item Senior Economist, 2008--2011.
\end{itemize2}

\smallskip

\item \textbf{Federal Reserve Bank of New York}
\begin{itemize2}
  \item Economist, 2004--2008.
\end{itemize2}
\end{itemize2}

\section*{Publications}

\begin{itemize}

\item ``Geometric Methods for Finite Rational Inattention,'' with Mich\`ele M\"uller-Itten and Zachary Stangebye, \textit{Quantitative Economics}, 15(1), pp. 115-144, 2024.

\item ``A Model of the Federal Funds Market: Yesterday, Today, and Tomorrow,'' with Gara Afonso and Ben Lester, {\it Review of Economic Dynamics}, 33, pp. 177-204, 2019.

\item ``The Perils of Nominal Targets,'' {\it Review of Economic Studies}, 85(1), pp. 50-86, 2018.

\item ``Taxes and Capital Structure: Understanding Firms' Savings,'' with Viktoria Hnatkovska, {\it Journal of Monetary Economics}, 87, pp. 13-33, 2017.

\item ``Excess Reserves and Monetary Policy Implementation,'' with Ben Lester, {\it Review of Economic Dynamics}, 23, pp. 212-235, 2017.

\item ``A Balls-and-Bins Model of Trade: Reply,'' with Mikl\'os Koren, {\it American Economic Review}, 106(3), pp. 852-854, 2016.

\item ``Sustainable Monetary Policy and Inflation Expectations,'' {\it B.E. Journal of Macroeconomics}, 16 (2), pp. 301-334, 2016.

\item ``Economies of Scale and the Size of Exporters,'' with Mikl\'os Koren, {\it Journal of the European Economic Association}, 13(3), pp. 482-511, 2015.

\item ``A Balls-and-Bins Model of Trade,'' with Mikl\'os Koren, {\it American Economic Review}, 104(7), pp. 2127-51, 2014.

\item ``Fraud Deterrence in Dynamic Mirrleesian Economies,'' with Thomas Mertens, {\it Journal of Monetary Economics}, 60(2), pp. 139-151, 2013.

\item ``Intertemporal Distortions in the Second Best,'' with Stefania Albanesi, {\it Review of Economic Studies}, 79(4), pp. 1271-1307, 2012.

\item ``Accounting for Development through Investment Prices,'' with Amartya Lahiri, {\it Journal of Monetary Economics}, 59 (6), pp. 550-564, 2012.

\item ``Credible Redistribution Policy and Skilled Migration,'' with Francesc Ortega, {\it European Economic Review} 55, pp. 228-245, 2011.

\item ``Credible Redistributive Policies and Migration across U.S. States,'' with Francesc Ortega, {\it Review of Economic Dynamics}, 13(2), pp. 403-423, 2010.

\item ``Of Nutters and Doves,'' with Martin Bodenstein, {\it The B.E. Journal of Macroeconomics}, 9(1), art. 35, 2009.
 
\item ``A Note on Incomplete Factor Taxation,'' {\it Journal of Public Economics}, 92 (10-11), pp. 2275-2281, 2008.

\item ``A General Theory (and Some Evidence) of Expectation Traps in Monetary Policy,'' {\it Journal of Money, Credit and Banking}, 40 (5), pp. 867-895, 2008. 

\item ``Can the U.S. Monetary Policy Fall (Again) in an Expectation Trap?'' with Martin Bodenstein, {\it Macroeconomic Dynamics}, 12 (5), pp. 664 -693, 2008.

\item ``Time Consistent Fiscal Policy and Heterogeneous Agents,'' {\it Review of Economic Dynamics}, 10 (1), pp. 31-54, 2007.

\item ``Equilibrium Selection through Incomplete Information in Coordination Games: An Experimental Study,'' with Antonio Cabrales and Rosemarie Nagel, {\it Experimental Economics}, 10 (3), pp. 221-234, 2007.

\end{itemize}

\section*{Working Papers}

\begin{itemize}
  \item ``Rational Inattention via Ignorance Equivalence,'' with Mich\`ele M\"uller-Itten and Zachary Stangebye. (Under revision at the \textit{Journal of Political Economy})
  \item ``Everything all the time? Entry and exit in U.S. Import Varieties,'' with Mikl\'os Koren.
  \item ``Bridges,'' with Mikl\'os Koren and D\'avid Kriszti\'an Nagy.
  \item ``On the Timing of Monetary Policy Reform,'' FRB Philadelphia Working Paper 13-4.
  \item ``Understanding Capital Taxation in Ramsey Models,'' with Stefania Albanesi.
\end{itemize}

\section*{Teaching Experience}

\begin{itemize}
  \item {\bf Guest Lectures on Monetary Policy and Implementation}
  \begin{itemize}
    \item Columbia University, Villanova University, Universitat Pompeu Fabra, Bank of Canada, Bank of England, among others.
  \end{itemize} 
  \item {\bf Northwestern University}
  \begin{itemize}
    \item Teaching Assistant, Graduate Macroeconomics, 2001-2002.
    \item \textit{Distinguished Teaching Award}, 2002.
  \end{itemize}
  \item {\bf Universitat Pompeu Fabra}
  \begin{itemize}
    \item Teaching Assistant, various courses, 1998-1999.
  \end{itemize}
  \item {\bf C.E.T.E.C.}
  \begin{itemize}
    \item Lecturer, Econometrics, 1998-1999.
  \end{itemize}
\end{itemize}

\section*{Selected Honors \& Awards}

\begin{itemize}
  \item Fellowship ``Fundaci\'on Rafael del Pino,'' 2002-2004.
  \item First Year Distinction Award, Northwestern University, 2000.
  \item Fellowship ``Fundaci\'o La Caixa,'' 1999-2001.
\end{itemize}

\section*{Recent Professional Activities and Services}

\subsection*{Conference Participation}
\begin{itemize}
  \item \textbf{Chair}, ``Tariffs and Free Trade Agreements,'' Allied Social Science Associations (ASSA) Annual Meeting, 2026.
  \item \textbf{Chair}, ``Consumer Spending during Inflation 2.0,'' National Association for Business Economics (NABE) Annual Meeting, 2026.
  \item \textbf{Session Chair}, ``Bank Balance Sheets and Liquidity,'' Wharton Liquidity Conference, 2024.
  \item \textbf{Panelist}, Bank of England BEAR Conference, 2025.
  \item \textbf{Panelist}, ``Annual State of the Economy,'' Chamber of Commerce for Greater Philadelphia, 2025.
  \item \textbf{Participant}, Jackson Hole Economic Policy Symposium, 2025.  
\end{itemize}

\subsection*{Short Notes \& Non-refereed Publications}
\begin{itemize}
  \item ``A Tractable Model of the Demand for Reserves Under Nonlinear Remuneration Schemes,'' FRB Philadelphia Working Paper 16-35, 2016. 
  \item ``On the Use of Market-Based Probabilities for Policy Decisions,'' FRB Philadelphia Working Paper 15-44, 2015.
  \item Various articles in \textit{Business Review} (2011, 2012, 2014, 2015).
\end{itemize}

\subsection*{Organization and Other Services}

\begin{itemize}
  \item Society for Computational Economics, Conference Program Committee.
  \item National Association for Business Economics (NABE), Research Committee Member.
  \item International Trade Workshop, FRB Philadelphia, Organizer.
  \item Federal Reserve ``Day-Ahead'' Conference on Financial Markets and Institutions, co-organizer.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}